Import and Tidy NSB Supplied Location and Haul-out Data

### 2021-11-02 data_raw/nsb/nsb_tidydata.Rmd

@@

>>>>

nsb_deployments2 <- tibble::tribble(
  ~speno, ~deployid, ~species, ~age, ~sex, ~tag_family, ~deploy_dt, ~end_dt,
  "EB2019BW02", 149452, "Bearded seal", "Pup", "Female", "SPLASH", "2019-09-19 18:30:00", "2020-05-24 17:30:00",
  "EB2019BW02", 171333, "Bearded seal", "Pup", "Female", "SPLASH", "2019-09-19 18:30:00", "2020-08-08 06:30:00"
) %>% 
  dplyr::mutate(deploy_dt = lubridate::ymd_hms(deploy_dt),
                end_dt = lubridate::ymd_hms(end_dt))

nsb_deployments <- dplyr::bind_rows(nsb_deployments, nsb_deployments2)

@@

nsb_timelines2 <- wcUtils::read_histos(
  here::here('data_raw/nsb/iceSeals_NSB_Alaska_vonDuyke_updatesOnly_20211008-Histos.csv'),
  dt_fmt = "%Y-%m-%d %H:%M:%S") %>% 
  wcUtils::tidyTimelines() %>% 
  dplyr::mutate(deployid = as.integer(deployid)) %>% 
  dplyr::filter(deployid %in% c(149452, 171333)) %>% 
  dplyr::select(-hist_type) %>% as_tibble()

nsb_timelines <- dplyr::bind_rows(nsb_timelines, nsb_timelines2)
